### 2023-01-19 paper_final.tex
Add files via upload

\documentclass[10pt,conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{url}
\makeatletter
\def\endthebibliography{%
	\def\@noitemerr{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist
}
\makeatother
\begin{document}

@@

	\begin{abstract}
		Blockchain technologies are a growing field of research and public interest. Second generation blockchains, like Ethereum, allow users to execute smart contracts, which are distributed applications executing user-defined logic. This not only expands the utility of blockchains, but also provides new opportunities for tools for solving the same issues that arise with conventional programs. Such tools include optimization of code, detecting code smells and vulnerabilites and developing automated code generation models among others. Such developments require the presence of a dataset of similar code which can be annotated and analyzed according to the desired end application. Existing sources of smart contract code include block explorers that provide limited search and retrieval capabilities on the single version of the contract deployed on the blockchain. Hence to aid the progress of research, this paper introduces the \textit{Smart Contract Repository}---a repository of publicly available Solidity smart contracts, complete with multiple versions of the same contract to help the analysis of the effects of incremental changes in source code.
	\end{abstract}

@@

	As Ethereum and similar second generation blockchains grow in popularity, the number of deployed smart contracts is growing in number, with the development of newer cryptocurrencies with an emphasis on financial inclusion. Smart contracts provide a way to generate new cryptocurrency tokens, known as \textit{application level tokens} on existing networks without the need to define a new protocol~\cite{commonshood}.\todo{Do we really need this last sentence here? Actually, I think that everything written from ``in number'' is not absolutely necessary, since it does not address the core topics of our work.}

	The defining feature of a blockchain is immutability, which makes it very difficult to alter smart contract code that has already been deployed. This raises the need to develop smart contract code that is error-free and efficient before deploying it on the blockchain~\cite{brandstatter}. Deployment and invocation of a smart contract on the blockchain leads to gas fees that are charged to the developer who deploys the smart contract and subsequently to the user who invokes the contract through a transaction~\cite{ethpaper}. This causes each smart contract to have a gas cost associated with it. The gas consumption can, in turn, also estimate the actual energy consumption of the smart contract, since the gas cost is proportional to the computation required for the contract operations~\cite{contractenergyconsumptionthesis}. Thus, it is important to deploy contracts which are error-free and efficient in order to reduce the costs to the user, as also to optimize the energy consumption.

	Source code repositories are an important aid to train systems that identify code smells and vulnerabilities. Code smells  are violations of fundamental design principles in the source code. Code smells can thus, apart from introducing errors in the code, also lead to suboptimal performance and efficiency. Code can further be optimized for maintainability, reusability, comprehensibility and extensibility~\cite{codesmellmining}. Apart from this, versions of the same source code can also provide an insight into the change of performance of the software over consecutive versions~\cite{softwareversion}.

	Code mining approaches involve detecting patterns from a repository of source files and analyzing the purpose those patterns serve. Existing code mining approaches mainly involve extracting business logic, automating the translation of code in one language to another, provisioning searching and indexing source files, detecting similarities (used primarily in detecting code smells), to summarize and visualize algorithms and also to extract and analyze information from source code metadata~\cite{codeminingsurvey}.\todo{There is a little bit of a logical gap between this paragraph and the next one. Here, you write about general code mining, in the next about optimization. Try to bridge that gap a little bit.}

	However, the principal difference between optimizing conventional programs and smart contracts lies in the fact that smart contracts have to be optimized primarily in terms of the gas cost~\cite{superoptimization}. The smart contract code, when deployed on the Ethereum network, is compiled into \textit{bytecode}. The bytecode is a string made of concatenated op-codes that are executed in sequence when the smart contract is invoked~\cite{wood2019ethereum}. The execution of each opcode is associated with a certain energy consumption, which is calculated and charged from the user according to the EVM \textit{gas model} ~\cite{wood2019ethereum}. This means that optimizing and analyzing smart contracts need to be done not only at the level of the source code, but also at the corresponding bytecode. Optimizing smart contract code directly implies optimizing the gas cost through the bytecode. This introduces an additional constraint and hence requires techniques for constraint-optimized pattern recognition \cite{utilitypattern}.\todo{Since the current version of the repository does not provide the bytecode, do we really want to highlight it here. Also, again, there is a logical/storyline gap between this paragraph and the next one, which should be bridged.}

@@

	Apart from code smell detection and optimization for smart contracts, which is our primary research direction, we believe that this repository can be helpful to researchers in a wide range of other application areas. For instance, code recommendation systems use publicly available code on the Internet to suggest usable pieces of source code to software developers. With the recent progress and development of large language models (LLMs), code generation models such as Codex~\cite{codex} are being used by developers to speed up software design and development, and are proving to be a viable business models for companies. Apart from recommender models focused on source code, general purpose LLMs such as ChatGPT, which is a version of GPT-3 fine-tuned for factoring in human feedback~\cite{chatgpt} also use large datasets of source code in order to make the token embeddings as generalized and diverse as possible~\cite{thestack}. Such models can also be used for code and algorithm summarization and visualization~\cite{codesummarization}. In security research, commits of source code repositories can be used to analyze patterns in smart contract code that eliminate or introduce certain vulnerabilities~\cite{securitydataset}. A dataset of source code can also be used to evaluate and benchmark the performance of static and dynamic analysis tools, which can also be used to detect software vulnerabilities~\cite{staticanalysis}. Analysis of code repositories can also provide useful to generate developer guidelines on writing clean and maintainable code~\cite{maintainablecode}, in the evaluation of software test methods\cite{testmethodevaluation}, in the structural and stylistic comparison of code written in different environments~\cite{codestylecomparison} and in many other studies. \todo{Very fine abstract, showing the need for the work at hand. However, again a logical gap to the next paragraph (i.e., the one about Ethereum).}

	The multitude of potential research areas which are based on source code shows the need for the Smart Contract Repository presented in the work at hand.\todo{Please extend this paragraph by writing down what we are actually delivering in this paper.}

	Ethereum was the first blockchain to introduce smart contracts and the high-level language Solidity to program smart contracts in. Solidity has grown to be the most mature and popular programming language for smart contracts~\cite{soliditycheck}. A majority of the contracts available on GitHub is written for the Ethereum blockchain, in Solidity~\cite{empiricalgithubcontracts}\todo{I do not see that the referenced paper shows this.}, and hence, Solidity was the language of choice in preparing the dataset\todo{Since it is not described yet what the paper will deliver, the reader actually does NOT know what this ``dataset'' is referring to. If I just read this particular paragraph, I would think that only a dataset is delivered (what we do not do!).}.  The dataset is compiled by crawling through and scraping publicly accessible repositories on GitHub that have Solidity as the main language. The repositories are identified and all available commits of each file are downloaded using the GitHub API. Due to the varying licenses of GitHub repositories, the dataset is being distributed in the form of a Python script which can be run to scrape GitHub and prepare the dataset in an SQLite database. During experimentation, the script collected 163,961 files from 1021 repositories.\todo{I do not like this paragraph too much, since it mixes things up quite a lot. First, it tries to justify why Solidity is used, which is fine (however, better grounding in the literature is necessary). However, afterwards, there is a mixture of repository functionalities and outcomes in terms of the the collected files. Please separate these parts better; this shows also again that it is necessary to first clearly describe what this paper is going to deliver. On another note: I also do not think that the problem with the licenses is highlighted here in enough detail. It's actually mentioned only very very briefly. I do not know if this is taken up later on again, but from I read here, I would not understand (as a normal reader) why there is actually a need for the script at all.}

	The remainder of this paper is structured as follows: In Section~\ref{sec:prelims}, we define  prerequisites for our approach. 	Afterwards, Section~\ref{sec:related} discusses the relevant and existing work, Section~\ref{sec:requirements} analyses the requirements for preparing the repository, Section~\ref{sec:implementation} describes how the script\todo{Again, I am not sure if it is too good to write here about the ``script'' alone.} was implemented and how it generates and stores the repository. Finally, Section~\ref{sec:limitations} discusses some limitations of the existing approach and Section~\ref{sec:conclusion} concludes the paper and lays the foundation for future work.

@@

	\subsection{Blockchain:}
	The blockchain technology was introduced by Satoshi Nakamoto in the Bitcoin White Paper \cite{bitcoinpaper}. A blockchain is a tamper-proof distributed ledger, which is similar to a distributed storage of transactions \cite{bitcoinbook} that represent interactions between users. Every transaction is registered in the ledger and the ledger is accessible to all users, thereby making it transparent. The ledger is a chain or immutable blocks which are made tamper-proof using cryptographic techniques. According to Dannen \cite{bitcoinbook}, the blockchain is a combination of the key concepts of Peer-to-peer networking, asymmetric cryptography and cryptographic hashing. Each block in a chain contains a set of transactions along with the hash of the previous block, which links blocks together and makes modification very difficult \cite{bitcoinpaper}. Every block also contains a nonce that is generated along with the block, by solving a hard cryptographic puzzle. This nonce makes it difficult for malicious parties to add blocks to the chain. Transactions are combined into blocks by \textit{miners}.

@@

	\subsection{Smart Contracts}
	In the original Ethereum paper, Buterin described smart contracts as ``systems which automatically move digital assets according to arbitrary pre-specified rules''\todo{I've replaced the quotation marks, but please check how to set them properly in LaTeX (Actually, your IDE shoudl do that for you)}\cite{ethpaper}. A smart contract is a program, that resides on the blockchain and is executed every time a user interacts with it. According to Dannen, smart contracts run business logic and enforce payment agreements between parties \cite{bitcoinbook}. Albert et al. have defined a smart contract from a more technical perspective as a collection of code (its functions) and data (its state) that resides at a specific address on the Ethereum blockchain \cite{gasol}.

@@

	A smart contract can be written in various high-level languages, but is complied into bytecode when deployed on the blockchain. For example, Ethereum introduces the programming language called Solidity, which can used to write smart contracts which are then run on the Ethereum Virtual Machine (EVM). The EVM is a quasi-Turing complete machine \cite{wood2019ethereum} in that it restricts the over-utilisation of resources by limiting the \textit{gas cost}. Each transaction on the Ethereum network has an associated gas consumption, which has to be paid for by the initiator of the transaction. A smart contract is essentially a collection of operations that incur gas cost \cite{wood2019ethereum}. Hence the deployment and invocations of a smart contract have gas consumption associated with them.

@@

	Code mining can therefore include different techniques and tools and is applicable to achieve different goals. Pham et al. find that it can be used “to help understanding, analysing, transforming, improving, maintaining or evolving a particular system, or to improve best practices for the development of new systems” \cite{treemining}. Hence, it is a promising approach to use code mining in the field of gas cost optimization of smart contracts.

@@

	%To the best of our knowledge, the analysis of smart contract code has only gained relatively little attention by the research community so far.

	There are a number of according approaches for the optimization of gas cost of smart contracts, which we discuss in the following.

@@

	Brandstätter et al. \cite{brandstatter} explored optimization strategies to implement a rule-based Solidity source code optimizer. The authors conclude that automatic rule detection and optimization need to be extended. Chen et al. have published multiple papers regarding the gas cost optimization of smart contracts \cite{chen1devour, chen2gaschecker, chen3soda, chen4stan}. Starting in 2017, they were one of the first to address the problem of gas optimization. They identified seven antipatterns in Solidity bytecode and presented the tool GASPER to identify three of these gas-costly patterns~\cite{chen1devour}. In 2018, they presented an in-depth investigation and the GasReducer tool, which can automatically check bytecode and run bytecode-to-bytecode optimization for 24 under-optimized code patterns. In 2020, the tools SODA \cite{chen3soda} and GasChecker~\cite{chen2gaschecker} followed, again dedicated to optimize bytecode based on pre-defined rules and patterns.

	Nagele et al. presented the SuperOptimizer \textit{ebso} in 2020. Using techniques of a Satisfiability Modulo Theories (SMT) solver, they developed and tested a tool that can run EVM bytecode optimizations \cite{nagele}. In 2017\todo{As written before, rather do not provide any years/dates in the running text. The exception is the work by Chen et al., since this tells a nice story.. I would not do that for Albert et al., even though they also have two papers. }, Albert et al. presented EthIR, ``a framework for analyzing Ethereum bytecode'' \cite{ethir}. EthIR is an extension of OYENTE that was published by Luu et al. \cite{oyente}. OYENTE is a symbolic execution tool that works with smart contract bytecode and detects bugs for pre-deployment mitigation. It uses the Z3 theorem solver~\cite{z3solver} for symbolic execution of the smart contract code~\cite{oyente}. In 2020, Albert et al. introduced the Eclipse\footnote{Eclipse IDE: https://www.eclipse.org/ide/} plugin GASOL that allows the user to investigate and optimize their Solidity code with different cost models \cite{gasol}.

	Most of the published work in the field of optimization of smart contracts focus on the analysis of the compiled bytecode and on detecting similarities between the source code and predefined patterns that can indicate vulnerabilities and malicious constructs. There has been limited research on deriving those patterns from a\todo{Something is wrong here} automatically, which could lead to the automation of existing optimization possibilities while providing opportunities for previously undetected optimization patterns.  Instead, the existing attempts at automating the optimization of smart contracts mainly utilize static and dynamic analysis of the smart contract source code or bytecode\todo{Is this sentence really necessary? It sounds like a little bit of a repetition}.\todo{Logical gap here again: Why is the third paper from Albert et al. mentioned here? The framing is not really good. Or should there be a paragraph before starting with the dicussion of the third Albert et al. paper?} In 2022, Albert et al. published another tool called Syrup~\cite{superoptimization} that is aimed at optimizing smart contracts based on an analysis of the blocks in the Control Flow Graph. The tool breaks up each block into sub-blocks based on state-modifying instructions and sends each sub-block to a Max-SMT solver such as Z3~\cite{z3solver} to obtain an optimized version of the sub-block~\cite{superoptimization}. Feist et al. published Slither, a framework for static analysis of smart contracts. Slither provides information regarding the performance, accuracy and robustness of smart contracts. However, the static analysis is less focused on the gas cost~\cite{slither}. Di Angelo et al. released an investigation and listing of 27 different tools designed to analyze smart contracts \cite{diangelo}. They concluded that the research community was in need of an open source benchmark suite of smart contracts. Chunmiao Li proposed optimization techniques for smart contracts using machine learning and deep learning techniques to estimate the gas consumption of specific types of constructs, such as loops and storage manipulation~\cite{chunmiaoli}.

	As is evident from the previous discussion, a reasonably large repository of smart contracts such as the one presented in this paper is essential, both for deriving new approaches to automatically optimizing smart contracts and for evaluating and benchmarking such tools. Using such a repository combined with static analysis of smart contracts can provide additional patterns that can be used to optimize new contracts, without depending on fixed rules or the optimization capability of SMT solvers.

	In the domain of repositories of smart contracts, Pierro et al. developed the Smart-Corpus software that creates a repository of verified smart contracts extracted from Etherscan and allows the download of and computation of metrics on the contracts in the repository~\cite{smartcorpus}. Other repositories, such as the ones by Ren et. al.~\cite{renrepo}, Ferreira et. al.~\cite{ferreirarepo} and SCRAWLD~\cite{scrawld} all contain deployed versions of smart contracts or synthetic smart contracts and do not have associated version histories. The Smart Contract Repository presented in this paper is distinct and novel in that it includes metadata as well as the complete version history of each contract and is not limited to a particular use case. Thus, this repository can prove useful to all use cases mentioned in this section.

	Apart from improving other smart contracts, a repository can also benefits researching conducting\todo{''researching conducting''? Is this correct?} studies on contract design patterns. For example, Wöhrer et al. presented recommendations for the development of smart contracts closely connected to the money transferring fashion of smart contracts~\cite{wohrer}. In 2020\todo{Again, please get rid of the years. This is never done.}, Marchesi et al. presented 24 design patterns for smart contracts categorized based on their features \cite{marchesi}. While most of such studies are based on manual inspection of existing smart contracts, a corpus of smart contracts may be helpful in automating the detection of such patterns and potentially analyzing their effects on gas cost. Additionally, evaluating and designing new programming languages aimed at providing predictable gas consumption with efficient bytecode, requires a dataset of smart contracts\todo{The final sentence is for sure correct, but do you have a reference for this?}.

	As mentioned in Section~\ref{sec:intro}, many applications developed for conventional code can be extended to smart contracts with training and evaluation on the proposed dataset.  Recommendation systems such as HelpMeOut~\cite{helpmeout}, ParseWeb~\cite{parseweb} and others could be trained to recommend snippets of Solidity code. LLMs focused on code, such as Codex \cite{codex} could be trained on the repository to work with smart contracts to add to its capabilities. In security research, apart from analysing individual deployed smart contracts, their version histories stored in the repository could be used to detect patterns that introduce or resolve vulnerabilities extending the work done, e.g., in~\cite{securitydataset}. Since the programming languages used in writing smart contracts are high-level languages similar to conventional programming languages, most of the existing tools and research can be extended to smart contracts. A complete repository of source code is the first step in achieving that aim. Our repository aims to fill that gap and provide researchers with complete information regarding smart contract source code and their versions. This repository is different from the repository of smart contracts that can be obtained from existing APIs, such as those provided by Etherscan\footnote{https://etherscan.io/}, since such APIs can only provide a single version of a smart contract deployed on the blockchain.
	\todo{The RW section is in general well-written, but there are some unwanted repetitions. For instance, you should discuss the weaknesses of Etherscan when it is mentioned the first time. Not start discussing it, then do something else, then go back to Etherscan. This is just one example - paper text should have also a high cohesion and loose coupling, just like code.}

@@

	In order to follow the best practices for creating a repository, a number of approaches for collecting datasets were studied. One of the best examples of preparing a large scale dataset from GitHub repositories can be found in \cite{thestack}. In the area of smart contracts, repositories can be found in the works of \cite{ren},\todo{Broken reference} \cite{ferreirarepo} and others. Similar to these datasets, our repository should contain the source code of all available contracts. Apart from the source files themselves, additional features need to be incorporated through the storage of metadata about the smart contracts, in order to provide researchers with complete information and to reduce the amount of pre-processing required before analyzing the code in the repository. Also, multiple versions of the source code, if available, can be used to compare incremental changes to the gas consumption and also to detect the introduction to vulnerabilities through changes in the source code. The metadata may include the name of the contract, a description of what it is intended for, details about the source repository, the compiler versions used to generate the bytecodes and also the commit messages, which can be helpful in manual annotation of changes. As mentioned in \cite{thestack}, the repository creation procedure should take into account repository licenses, particularly if the repository is to be made publicly available. The repository should be able to filter out files without permissive licenses.

@@

	\todo{As discussed today, and also mentioned above: I am clearly missing a discussion of the need for the script. The reviewers will not understand why it is needed. We need a paragraph on this, clearly giving this information.}

>>>>

\documentclass[10pt,conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{url}
\usepackage{hyperref}
\makeatletter
\def\endthebibliography{%
	\def\@noitemerr{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist
}
\makeatother
\begin{document}

@@

	\begin{abstract}
		Blockchain technologies are a growing field of research and public interest. Second generation blockchains, like Ethereum, allow users to execute smart contracts, which are distributed applications executing user-defined logic. This not only expands the utility of blockchains, but also provides new opportunities for tools for solving the same issues that arise with conventional programs. Such tools include optimization of code, detecting code smells and vulnerabilities and developing automated code generation models among others. Such developments require the presence of a dataset of similar code which can be annotated and analyzed according to the desired end application. Existing sources of smart contract code include block explorers that provide limited search and retrieval capabilities on the single version of the contract deployed on the blockchain. Hence, to aid the progress of research, this paper introduces the \textit{Smart Contract Repository}---a repository of publicly available Solidity smart contracts, complete with multiple versions of the same contract to help the analysis of the effects of incremental changes in source code.
	\end{abstract}

@@

	As Ethereum and similar second generation blockchains grow in popularity, the number of deployed smart contracts is growing in number. The defining feature of a blockchain is immutability, which makes it very difficult to alter smart contract code that has already been deployed. This raises the need to develop smart contract code that is error-free and efficient before deploying it on the blockchain~\cite{brandstatter}. Deployment and invocation of a smart contract on the blockchain leads to gas fees that are charged to the developer who deploys the smart contract and subsequently to the user who invokes the contract through a transaction~\cite{ethpaper}. This causes each smart contract to have a gas cost associated with it. The gas consumption can, in turn, also estimate the actual energy consumption of the smart contract, since the gas cost is proportional to the computation required for the contract operations~\cite{contractenergyconsumptionthesis}. Thus, it is important to deploy contracts which are error-free and efficient in order to reduce the costs to the user, as also to optimize the energy consumption.

	Source code repositories are an important aid to train systems that identify code smells and vulnerabilities. Code smells are violations of fundamental design principles in the source code. Code smells can thus, apart from introducing errors in the code, also lead to sub-optimal performance and efficiency. Code can further be optimized for maintainability, re-usability, comprehensibility and extensibility~\cite{codesmellmining}. Apart from this, versions of the same source code can also provide an insight into the change of performance of the software over consecutive versions~\cite{softwareversion}.

	Code mining approaches involve detecting patterns from a repository of source files and analyzing the purpose those patterns serve. Existing code mining approaches mainly involve extracting business logic, automating the translation of code in one language to another, provisioning searching and indexing source files, detecting similarities (used primarily in detecting code smells), to summarize and visualize algorithms and also to extract and analyze information from source code metadata~\cite{codeminingsurvey}. The summarization and visualization of algorithms using code mining can also be extended to search for optimizing patterns in smart contracts. Training of such code mining approaches requires the availability of a large dataset.

	However, the principal difference between optimizing conventional programs and smart contracts lies in the fact that smart contracts have to be optimized primarily in terms of the gas cost~\cite{superoptimization}. The smart contract code, when deployed on the Ethereum network, is compiled into \textit{bytecode}. The bytecode is a string made of concatenated op-codes that are executed in sequence when the smart contract is invoked~\cite{wood2019ethereum}. The execution of each opcode is associated with a certain energy consumption, which is calculated and charged from the user according to the EVM \textit{gas model} ~\cite{wood2019ethereum}. This means that optimizing and analyzing smart contracts need to be done not only at the level of the source code, but also at the corresponding bytecode. Optimizing smart contract code directly implies optimizing the gas cost. This introduces an additional constraint and hence requires techniques for constraint-optimized pattern recognition \cite{utilitypattern}.

@@

	Apart from code smell detection and optimization for smart contracts, which is our primary research direction, we believe that this repository can be helpful to researchers in a wide range of other application areas. For instance, code recommendation systems use publicly available code on the Internet to suggest usable pieces of source code to software developers. With the recent progress and development of large language models (LLMs), code generation models such as Codex~\cite{codex} are being used by developers to speed up software design and development, and are proving to be a viable business model for companies. Apart from recommender models focused on source code, general purpose LLMs such as ChatGPT, which is a version of GPT-3 fine-tuned for factoring in human feedback~\cite{chatgpt} also use large datasets of source code in order to make the token embeddings as generalized and diverse as possible~\cite{thestack}. Such models can also be used for code and algorithm summarization and visualization~\cite{codesummarization}. In security research, commits of source code repositories can be used to analyze patterns in smart contract code that eliminate or introduce certain vulnerabilities~\cite{securitydataset}. A dataset of source code can also be used to evaluate and benchmark the performance of static and dynamic analysis tools, which can also be used to detect software vulnerabilities~\cite{staticanalysis}. Analysis of code repositories can also prove useful in generating developer guidelines on writing clean and maintainable code~\cite{maintainablecode}, in the evaluation of software test methods\cite{testmethodevaluation}, in the structural and stylistic comparison of code written in different environments~\cite{codestylecomparison} and in many other studies. Given the high utility value of code mining on a available repositories, we believe that these algorithms can be extended to smart contracts running on second generation blockchains such as Ethereum using the dataset introduced in this paper.

	The dataset in this paper is being distributed in the form of a python script, which, when run, scrapes GitHub repositories containing Solidity code. GitHub allows a wide range of licenses on its repositories. GitHub allows multiple licensing schemes to be applied to its repositories. Among the repositories accessible in the public domain, \textit{copyleft} licensed files and files with \textit{permissive} licenses still require attribution to the original creators and in some cases distribution only under the specified terms in the license. Only files with \textit{open-source} licenses can be distributed without any licensing concerns. To avoid these issues, we do not provide the data, but only the script that generates the dataset. The script will create an SQLite database on the user's local machine that will then contain the files in each repository together with their commit history and metadata. The SQLite database can be accessed using existing tools to read and manipulate SQLite databases and also through SQL queries.

	Ethereum was the first blockchain to introduce smart contracts and the high-level language Solidity to program smart contracts in. Solidity has grown to be the most mature and popular programming language for smart contracts~\cite{soliditycheck}. GitHub has a high number of projects with smart contracts for Ethereum, a large number of them being written in Solidity ~\cite{empiricalgithubcontracts}. During experimentation, the script collected 163,961 files from 1021 repositories.

	The remainder of this paper is structured as follows: In Section~\ref{sec:prelims}, we define  prerequisites for our approach. 	Afterwards, Section~\ref{sec:related} discusses the relevant and existing work,
	 Section~\ref{sec:requirements} analyses the requirements for preparing the repository, Section~\ref{sec:implementation} describes how the dataset can be generated. Finally, Section~\ref{sec:limitations} discusses some limitations of the existing approach and Section~\ref{sec:conclusion} concludes the paper and lays the foundation for future work.

@@

	\subsection{Blockchain:}
	The blockchain technology was introduced by Satoshi Nakamoto in the Bitcoin White Paper \cite{bitcoinpaper}. A blockchain is a tamper-proof distributed ledger, which is similar to a distributed storage of transactions \cite{bitcoinbook} that represent interactions between users. Every transaction is registered in the ledger and the ledger is accessible to all users, thereby making it transparent. The ledger is a chain of immutable blocks which are made tamper-proof using cryptographic techniques. According to Dannen \cite{bitcoinbook}, the blockchain is a combination of the key concepts of Peer-to-peer networking, asymmetric cryptography and cryptographic hashing. Each block in a chain contains a set of transactions along with the hash of the previous block, which links blocks together and makes modification very difficult \cite{bitcoinpaper}. Every block also contains a nonce that is generated along with the block, by solving a hard cryptographic puzzle. This nonce makes it difficult for malicious parties to add blocks to the chain. Transactions are combined into blocks by \textit{miners}.

@@

	\subsection{Smart Contracts}
	In the original Ethereum paper, Buterin described smart contracts as ``systems which automatically move digital assets according to arbitrary pre-specified rules''\cite{ethpaper}. A smart contract is a program, that resides on the blockchain and is executed every time a user interacts with it. According to Dannen, smart contracts run business logic and enforce payment agreements between parties \cite{bitcoinbook}. Albert et al. have defined a smart contract from a more technical perspective as a collection of code (its functions) and data (its state) that resides at a specific address on the Ethereum blockchain \cite{gasol}.

@@

	A smart contract can be written in various high-level languages, but is complied into bytecode when deployed on the blockchain. For example, Ethereum introduces the programming language called Solidity, which can used to write smart contracts, that are then run on the Ethereum Virtual Machine (EVM). The EVM is a quasi-Turing complete machine \cite{wood2019ethereum} in that it restricts the over-utilization of resources by limiting the \textit{gas cost}. Each transaction on the Ethereum network has an associated gas consumption, which has to be paid for by the initiator of the transaction. A smart contract is essentially a collection of operations that incur gas cost \cite{wood2019ethereum}. Hence the deployment and invocations of a smart contract have gas consumption associated with them.

@@

	Code mining can therefore include different techniques and tools and is applicable to achieve different goals. Pham et al. find that it can be used “to help understanding, analyzing, transforming, improving, maintaining or evolving a particular system, or to improve best practices for the development of new systems” \cite{treemining}. Hence, it is a promising approach to use code mining in the field of gas cost optimization of smart contracts.

@@

	There are a number of according approaches for the optimization of gas cost of smart contracts, which we discuss in this section.

@@

	Brandstätter et al. \cite{brandstatter} explored optimization strategies to implement a rule-based Solidity source code optimizer. The authors conclude that automatic rule detection and optimization need to be extended. Chen et al. have published multiple papers regarding the gas cost optimization of smart contracts \cite{chen1devour, chen2gaschecker, chen3soda, chen4stan}. Starting in 2017, they were one of the first to address the problem of gas optimization. They identified seven anti-patterns in Solidity bytecode and presented the tool GASPER to identify three of these gas-costly patterns~\cite{chen1devour}. In 2018, they presented an in-depth investigation and the GasReducer tool, which can automatically check bytecode and run bytecode-to-bytecode optimization for 24 under-optimized code patterns. In 2020, the tools SODA \cite{chen3soda} and GasChecker~\cite{chen2gaschecker} followed, again dedicated to optimize bytecode based on pre-defined rules and patterns.

	Nagele et al. presented the SuperOptimizer \textit{ebso}. Using techniques of a Satisfiability Modulo Theories (SMT) solver, they developed and tested a tool that can run EVM bytecode optimizations \cite{nagele}. Albert et al. presented EthIR, ``a framework for analyzing Ethereum bytecode'' \cite{ethir}. EthIR is an extension of OYENTE that was published by Luu et al. \cite{oyente}. OYENTE is a symbolic execution tool that works with smart contract bytecode and detects bugs for pre-deployment mitigation. It uses the Z3 theorem solver~\cite{z3solver} for symbolic execution of the smart contract code~\cite{oyente}. Albert et al. introduced the Eclipse\footnote{Eclipse IDE: https://www.eclipse.org/ide/} plugin GASOL that allows the user to investigate and optimize their Solidity code with different cost models \cite{gasol}.

	The published work discussed till now focus on the analysis of the compiled bytecode and on detecting similarities with predefined patterns that can indicate vulnerabilities and malicious constructs. There has been limited research on deriving those patterns from source code automatically, which could lead to the automation of existing optimization possibilities while providing opportunities for previously undetected optimization patterns. Such existing approaches tend to utilize static and symbolic execution of the code to find possible chances at optimization or to refactor the sequence of operations to reduce storage manipulation related gas consumption. One of such approaches is Syrup~\cite{superoptimization} by Albert et al., that is aimed at optimizing smart contracts based on an analysis of the blocks in the Control Flow Graph. The tool breaks up each block into sub-blocks based on state-modifying instructions and sends each sub-block to a Max-SMT solver such as Z3~\cite{z3solver} to obtain an optimized version of the sub-block~\cite{superoptimization}. Feist et al. published Slither, a framework for static analysis of smart contracts. Slither provides information regarding the performance, accuracy and robustness of smart contracts. However, the static analysis is less focused on the gas cost~\cite{slither}. Di Angelo et al. released an investigation and listing of 27 different tools designed to analyze smart contracts \cite{diangelo}. They concluded that the research community was in need of an open source benchmark suite of smart contracts. Chunmiao Li proposed optimization techniques for smart contracts using machine learning and deep learning techniques to estimate the gas consumption of specific types of constructs, such as loops and storage manipulation~\cite{chunmiaoli}.

	The evaluation and training of the approaches mentioned in the previous discussion require a reasonably large repository of smart contracts such as the one presented in this paper. Using such a repository combined with static analysis of smart contracts can provide additional patterns that can be used to optimize new contracts, without depending on fixed rules or the optimization capability of SMT solvers.

	Apart from improving other smart contracts, a repository can also benefit researchers conducting studies on contract design patterns. For example, Wöhrer et al. presented recommendations for the development of smart contracts closely connected to the money transferring fashion of smart contracts~\cite{wohrer}. Marchesi et al. presented 24 design patterns for smart contracts categorized based on their features \cite{marchesi}. While most of such studies are based on manual inspection of existing smart contracts, a corpus of smart contracts may be helpful in automating the detection of such patterns and potentially analyzing their effects on gas cost. Additionally, a dataset of smart contracts may be used for evaluating and designing new programming languages aimed at providing predictable gas consumption with efficient bytecode.

	As mentioned in Section~\ref{sec:intro}, many applications developed for conventional code can be extended to smart contracts with training and evaluation on the proposed dataset.  Recommendation systems such as HelpMeOut~\cite{helpmeout}, ParseWeb~\cite{parseweb} and others could be trained to recommend snippets of Solidity code. LLMs focused on code, such as Codex \cite{codex} could be trained on the repository to work with smart contracts to add to its capabilities. In security research, apart from analyzing individual deployed smart contracts, their version histories stored in the repository could be used to detect patterns that introduce or resolve vulnerabilities extending the work done, e.g., in~\cite{securitydataset}. Since the programming languages used in writing smart contracts are high-level languages similar to conventional programming languages, most of the existing tools and research can be extended to smart contracts. A complete repository of source code is the first step in achieving that aim. Our repository aims to fill that gap and provide researchers with complete information regarding smart contract source code and their versions.

	In the domain of repositories of smart contracts, Pierro et al. developed the Smart-Corpus software that creates a repository of verified smart contracts and allows the download of and computation of metrics on the contracts in the repository~\cite{pierro}. Other repositories, such as the ones by Ren et al.~\cite{renrepo}, Ferreira et al.~\cite{ferreirarepo} and SCRAWLD~\cite{scrawld} all contain deployed versions of smart contracts or synthetic smart contracts and do not have associated version histories.

	Finally, there are multiple sources that can be used to generate a repository of smart contracts.  Pierro et al. list some sources that can be used to collect smart contract source code from the Web \cite{pierro}. These resources include commonly known code repository hosting platforms (GitHub\footnote{https://github.com}, GitLab\footnote{https://about.gitlab.com} and BitBucket\footnote{https://bitbucket.org}). Additionally, several Ethereum block explorers are available. These services allow for different kinds of interactions with and the analysis of the Ethereum blockchain. EtherScan\footnote{https://etherscan.io/} and EtherChain\footnote{https://etherchain.org/} are two examples of block explorers. In their paper, Pierro et al. use the API of textbf to collect verified smart contracts and store them in a database~\cite{pierro}. However, most of these block explorers do not make the source code of the contracts publicly accessible, neither do they offer access to multiple versions of the same contract, a limitation which arises from the immutability of the blockchain. Existing smart contract datasets use deployed versions of smart contracts from these block explorers and hence do not have access to the version history of the smart contracts. The Smart Contract Repository presented in this paper is distinct and novel in that it includes metadata as well as the complete version history of each contract and is not limited to a particular use case. Thus, this repository can prove useful to all use cases mentioned in this section.

@@

	In order to follow the best practices for creating a repository, a number of approaches for collecting datasets were studied. One of the best examples of preparing a large scale dataset from GitHub repositories can be found in \cite{thestack}. In the area of smart contracts, repositories can be found in the works of \cite{renrepo} \cite{ferreirarepo} and others. Similar to these datasets, our repository should contain the source code of all available contracts. Apart from the source files themselves, additional features need to be incorporated through the storage of metadata about the smart contracts, in order to provide researchers with complete information and to reduce the amount of pre-processing required before analyzing the code in the repository. Also, multiple versions of the source code, if available, can be used to compare incremental changes to the gas consumption and to detect the introduction of vulnerabilities through changes in the source code. The metadata may include the name of the contract, a description of what it is intended for, details about the source repository, the compiler versions used to generate the bytecodes and also the commit messages, which can be helpful in manual annotation of changes. As mentioned in \cite{thestack}, the repository creation procedure should take into account repository licenses, particularly if the repository is to be made publicly available. The repository should be able to filter out files without permissive licenses.

@@

	Finally, for use by the greater research community, the repository should be in a form that can be accessed and distributed freely. As discussed on Section \ref{sec:intro}, repositories can be licensed in multiple ways and have different modification and distribution requirements. It may not be possible to satisfy all such regulations while distributing a dataset made of files sourced from multiple repositories and by multiple developers and organizations. That is why the end user should be able to create the repository at their end and use it for their personal research. Hence, the ideal distribution medium for the repository would be a script in a widely used programming language that, when run, collects the required files and creates the repository in a database at the user's end.
